### 2016-07-21 generic.tex
generic

\subsection{Adversarial Soundness}
\heading{FP security.}
As highlighted by Naor and Yogev,
Equation~(\ref{eqn:correctness}) is a non-adaptive version of correctness;
we are interested in defining an adaptive (i.e., adversarial) notion
of correctness. \tsnote{Correctness?  Or soundness?}
The general style of the definition is as follows:
first, a set $S$ is chosen according to some distribution over~$\mathcal{S}$ and then
$\Rep(S)$ is run to generate $(\aux, M)$. (Unless stated otherwise, we assume
security holds for all distributions and thus for all sets $S$.)
The attacker $A$ is given $\aux$ and (possibly)~$S$;
in addition, $A$ is given \emph{oracle access} to~$\Qry(\aux, M, \cdot)$.
If $(\Rep, \Qry)$ is defined in the random-oracle model, then
$A$ is given access to the random oracle as well.
$A$ \emph{succeeds} if it outputs $t$ distinct queries $q_1, \ldots, q_t \in \mathcal{Q}$ for which
$\Qry(\aux, M, q_i) \neq q_i(S)$ for all~$i$.
Roughly, we say that a set-representation is $(t,\epsilon')$-FP-secure if the probability that
any polynomial-time attacker succeeds is at most~$\epsilon'$. A full definition
would also bound the number of queries to $\Qry$ (and the random oracle) made
be the attacker; it is useful to make the convention that if $A$ outputs
$q_1, \ldots, q_t$ then it must have made those queries to its oracle previously.

The notion of FP-security defined above captures the fp-prv notion for Bloom filters
if we put the hash
functions in $M$ (and thus increase the size of the set-representation); it also captures the fp-pub
notion if we put the hash function in~$\aux$. \tsnote{Except that the win condition allows both
false-positives and false-negatives, given the correctness requirement
in the syntax.} \jnote{True. But if false negatives cannot occur at all (by design of
the set-representation, not by definition of the primitive), then the attacker cannot hope to win
by finding a false negative.} It captures the fp-bb-pub notion in the
random-oracle model.

Note that the security we can hope for is somewhat limited, since there
is always a trivial attack in which
the attacker tries random queries $q_1, q_2, \ldots$ until it finds $t$ queries for which the
set-representation returns an incorrect answer.\footnote{This assumes the attacker
knows the true set $S$, which need not be the case.} Roughly speaking,
if the set-representation is $\epsilon$-correct then the attacker expects to find a query on which
an incorrect result is returned
every $1/\epsilon$ tries; thus, an
attacker making $t/\epsilon$ queries succeeds with constant probability.

@@

Actually, it seems worthwhile to formalize this. Let $X_i$ be a random variable indicating
whether the $i$th query of the attacker gives an incorrect result. Then an attacker making $T$
queries can succeed
if $N \stackrel{{\rm def}}{=} \sum_{i=1}^T X_i \geq t$. If we treat the $X_i$ as independent Bernoulli trials with
probability~$\epsilon$, then $N$ follows the well-studied binomial distribution.
Let $\bin(T, \epsilon; t)$ denote the probability that $N \geq t$. So the best security we can
hope for
is that if the set-representation is $\epsilon$-correct then for any desired bound $T$
the set-representation is $(t, \bin(T,\epsilon; t))$-FP-secure against any attacker making
at most $T$~queries. \jnote{Need to find different terms to use for a query $q \in \mathcal{Q}$
and a query that the attacker makes to its oracle.}

>>>>

\subsection{Adversarial Correctness}
\heading{FP security.}
As highlighted by Naor and Yogev,
Equation~(\ref{eqn:correctness}) is a non-adaptive version of correctness;
we are interested in defining an adaptive (i.e., adversarial) notion
of correctness.

The general style of the definition is as follows:
first, a set~$S$ is chosen according to some distribution over~$\mathcal{S}$ and then
$\Rep(S)$ is run to generate $(M,\aux)$. (Unless stated otherwise, we assume
security holds for all distributions and thus for all sets $S$.)
The attacker $A$ is given $\aux$ and (possibly)~$S$;
in addition, $A$ is given \emph{oracle access} to~$\Qry(M,\aux,\cdot)$.
If $(\Rep, \Qry)$ is defined in the random-oracle model, then~$A$ is given access to the random oracle as well.
The adversary \emph{succeeds} if it outputs~$t$ distinct queries $q_1, \ldots, q_t \in \mathcal{Q}$ for which
$\Qry(\aux, M, q_i) \neq q_i(S)$ for all~$i \in [t]$
\tsnote{I will typeset this into an experiment.}

Roughly, we say that a set-representation is $(t,\epsilon')$-FP-secure if the probability that
any polynomial-time attacker succeeds is at most~$\epsilon'$. \tsnote{$t$ might be a bad choice, since it looks like ``time''.}
A full definition would also bound the number of queries to $\Qry$ (and the random oracle) made
be the attacker; it is useful to make the convention that if~$A$ outputs
$q_1, \ldots, q_t$ then it must have made those queries to its oracle previously.

The notion of security defined above captures the fp-prv notion for Bloom filters
if we put the hash functions in~$M$ (and thus increase the size of the set-representation); it also captures the fp-pub
notion if we put the hash function in~$\aux$. 
%\tsnote{Except that the win condition allows both
%false-positives and false-negatives, given the correctness requirement
%in the syntax.} 
%\jnote{True. But if false negatives cannot occur at all (by design of
%the set-representation, not by definition of the primitive), then the attacker cannot hope to win
%by finding a false negative.} 
It captures the fp-bb-pub notion in the random-oracle model.

Note that the security we can hope for is somewhat limited, since there
is always a trivial attack in which
the attacker tries random queries $q_1, q_2, \ldots$ until it finds~$t$ queries for which the
set-representation returns an incorrect answer.\footnote{This assumes the attacker
knows the true set~$S$, which need not be the case.} Roughly speaking,
if the set-representation is $\epsilon$-correct then the attacker expects to find a query on which
an incorrect result is returned every $1/\epsilon$ tries; thus, an
attacker making $O(t/\epsilon)$ queries succeeds with constant probability (almost always).

@@

Actually, it seems worthwhile to formalize this. Let $X_i$ be a random variable indicating
whether the $i$th query of the attacker gives an incorrect result. Then an attacker making $T$
queries can succeed
if $N \stackrel{{\rm def}}{=} \sum_{i=1}^T X_i \geq t$. If we treat the $X_i$ as independent Bernoulli trials with
probability~$\epsilon$, then $N$ follows the well-studied binomial distribution.
Let $\bin(T, \epsilon; t)$ denote the probability that $N \geq t$. \tsnote{Viewed another way, we could let~$T$ be a negative binomial RV, and ask how many queries are needed (w.h.p) for $N \geq t$.} 
So the best security we can hope for
is that if the set-representation is $\epsilon$-correct then for any desired bound $T$
the set-representation is $(t, \bin(T,\epsilon; t))$-FP-secure against any attacker making
at most $T$~queries. \jnote{Need to find different terms to use for a query $q \in \mathcal{Q}$
and a query that the attacker makes to its oracle.}
